The Shape Matching Element Method for Meshless Animation of NURBs Models

### 2021-01-22 paper/sections/methods.tex
add section labels

Attempting to use $\Pmatx_i$ in~\refeq{shapematch} on a per-part basis is problematic as it can become ill-posed, especially for planar boundary representations. 
To alleviate this problem we invoke the \emph{hierarchical ordering principle}, which argues that the behavior of a system is typically 
dominated by lower order effects~\cite{li2006regularities}.

 \dave{heirarchical ordering to handle degenerecies}

\subsection{Meshless Blending Weight Computation}

>>>>

Attempting to use $\Pmatxi$ in~\refeq{shapematch} on a per-part basis is problematic as it can become ill-posed, especially for planar boundary representations. 
To alleviate this problem we invoke the \emph{hierarchical ordering principle}, which argues that the behavior of a system is typically 
dominated by lower order effects~\cite{li2006regularities}.

\subsection{Meshless Blending Weight Computation}
\label{sec:weights}
